\documentclass[10pt]{tufte-handout}

\usepackage{graphicx}
\setkeys{Gin}{width=\linewidth, totalheight=\textheight, keepaspectratio}
\graphicspath{{plots/}{./}}

% Adjust the bottom margin
\geometry{
 bottom = 2.5cm % Adjust this value to change the bottom margin
}
\usepackage{booktabs}
\usepackage{lipsum}

\usepackage{setspace}


\usepackage{xcolor} % Required for defining colors
\definecolor{red}{RGB}{148, 25, 4} % Define magenta color

\usepackage{hyperref} % Required for hyperlinks
\hypersetup{
 colorlinks = true,
 linkcolor = red, 	% Color of internal links
 urlcolor = red, 	% Color of URLs
 citecolor = red 	% Color of bibliographical citations
}

%%%%% %%%%% %%%%% %%%%%
\title{}																% Name
\date{} 																% Date, use \date{} for no date

\begin{document}

\maketitle 															% Print the title section

\vspace{0cm}

%%%%% %%%%% %%%%% %%%%%
\justifying

{\LARGE \textsc{\allcaps{José Á. Torrens Hernández}}} 			% Name

\vspace{1.5cm}

\setlength{\parindent}{0cm}

\small

{\normalsize\emph{Mexico City, January 29, 2024}} 		% Date

\vspace{1.5cm}

\spacing{1}

{\smallcaps{Scotiabank Mexico | Strategy and Transformation Department}				          % Company Name
% {\smallcaps{Department Name}\\				% Department Name
% {\normalsize Department Address}\\		% Department Adress
% {\normalsize City, ST., Zip Code}			% Adress

\vspace{1.5cm}

\spacing{1.15}

{\emph{Dear Hiring Team,}} 		% Hiring Team

\setlength{\parindent}{1cm}

%%%%% %%%%% %%%%% %%%%%
\begin{fullwidth}
\vspace{.2cm}

I am writing to express my interest in the \emph{Business Transformation Consultant} position at Scotiabank Mexico, as advertised on LinkedIn. As a last semester political science student at Instituto Tecnológico Autónomo de México (ITAM), I am motivated about the opportunity to bring my passion for data and public policy to the \emph{Strategy and Transformation} department at Scotiabank Mexico. I believe that my excellent communication skills and outstanding analytical and quantitative competencies will enable me to deliver superior value for the company's transformation. Moreover, I consider my knowledge on data science, economics, statistics, and public policy analysis will contribute to the team's objectives.

\vspace{.2cm}

I am confident that my experience as Regulatory Affairs and Institutional Relations Intern at Coca-Cola FEMSA, where I contribute to the company's risk management strategy by preparing policy briefs, executive presentations, reports, and other documents on key political risk identifications, will contribute to the Scotiabank transformation process.

\vspace{.2cm}

Before Coca-Cola FEMSA, I worked as a Research Assistant for Ph.D. Eric Magar Meurs at ITAM, where I sharpened my skills in R and RStudio and strengthened my ability to extract meaningful insights from complex datasets and contexts. This professional experience allowed me to develop the skills that Scotiabank is looking for in the \emph{Business Transformation Consultant} position. Additionally, my participation in the Evidence in Governance and Politics Latin America Regional Hub (EGAP 2023), under the guidance of Ph.D. Jake Bowers, University of Illinois Professor, and Marteen Voors, Associate Professor at the Development Economics Group, helped me improve my abilities in causal inference, randomized controlled trials, hypothesis testing, and impact evaluation.

\vspace{.2cm}

I am excited about the opportunity to contribute to the innovative work being done at Scotiabank and am eager to discuss how my skills and experiences can support the organization's objectives. My commitment to excellence, coupled with my drive for continual learning and growth, aligns seamlessly with the culture and values upheld by your organization. Scotiabank values of excellence, responsibility, respect, and corporate integrity line up with the principles that guide me every day and that have driven me throughout my career.

\vspace{.2cm}

Thank you and I look forward to hearing from you soon.
\end{fullwidth}

\vspace{.75cm}

\spacing{1}

\setlength{\parindent}{0cm}

\normalsize\textsc{\smallcaps{José Á. Torrens Hernández}}\\
{\emph{Ciudad de México}}\\
\contact{+52 55$\cdot$32$\cdot$46$\cdot$78$\cdot$20}\\
{\href{mailto://jose.torrens@itam.mx}{jose.torrens@itam.mx}}\\
{\href{https://www.linkedin.com/in/jtorrensh/}{in/jtorrensh}}\\
% {\href{https://github.com/pptrrns}{github/pptrrns}}}

\end{document}