\documentclass[letter]{resume}
\usepackage[letterpaper, 
            left = 1.5cm,
            top = 2cm,
            right = 1.5cm,
            bottom = 1.5cm]{geometry}

\usepackage{color}
\definecolor{teal}{RGB}{16, 96, 89}
\definecolor{azure}{rgb}{0.0, 0.5, 1.0}
\definecolor{red}{RGB}{148, 25, 4}
\usepackage[colorlinks = true,
            allcolors = red,
            pdfborderstyle = {/S/U/W 1}]{hyperref}

\usepackage{vwcol}
\usepackage{natbib}
\usepackage{cfr-lm}
\usepackage{graphicx}
\usepackage{upquote}

\usepackage{setspace}
\setstretch{1}
\clubpenalty = 10000
\widowpenalty = 10000

\begin{document}

%%%%% %%%%% %%%%% Title Section

\begin{center}
\name{José Á. Torrens Hernández}
\normalsize
\contact {+52 55$\cdot$32$\cdot$46$\cdot$78$\cdot$20}
{\href{mailto://jose.torrens@itam.mx}{jose.torrens@itam.mx}}
{\href{https://www.linkedin.com/in/jtorrensh/}{in/jtorrensh}}
{\href{https://github.com/pptrrns}{github/pptrrns}}
\bfseries{Political Scientist, Mexico City}

% {\emph{Intereses}: Política Pública, Inferencia Causal, Análisis de Datos, Asuntos Gubernamentales \emph{\&} Asuntos Públicos.}
% \vspace{0.05cm}
\end{center}

\spacing{1}

%%%%% %%%%% %%%%% Education

\section{Education}

\begin{content}
% \vspace{0.05cm}

{\bf Instituto Tecnológico Autónomo de México} \hfill{2018 -- 2023}\\ 
{B.A., \emph{Political Science}} \hfill \emph{CGPA: 3.5/4.0}

\sectionlineskip
\end{content}

%%%%% %%%%% %%%%% Experience

\section{Experience}

\begin{content}
% \vspace{0.05cm}

\begin{position}{Regulatory and Institutional Affairs Intern}{2022 -- present}{Coca--Cola FEMSA}{}{}
  \item Analysis and monitoring of regulatory trends in the bottled beverage industry across 10 Latin American countries, identifying key risks and opportunities for strategic decision-making.
  \item Prepared \emph{policy briefs}, presentations, reports, and other documents for the company's category defense strategy. These inputs include arguments in defense of the industry to mitigate regulatory trends that undermine business continuity.
  \item Generated situation reports, regulatory alerts, and comprehensive reports on regional and international political, economic, and social landscapes for \emph{C-suite} executives.
  \item Research on key individuals and institutions for the company's institutional relationship agenda.
\end{position}

\begin{position}{Research Assistant}{2022}{Eric Magar Meurs, Ph.D $\sim$ ITAM}{}{}
  \item Data collection, processing, and cleaning.
  \item Data management using Git and GitHub.
  \item Data analysis using computer software such as RStudio and CartoDB.
  \item Generated charts, maps, and plots to facilitate data analysis.
\end{position}
\vspace{-.1 \baselineskip}

\sectionlineskip
\end{content}

%%%%% %%%%% %%%%% Courses

\section{Courses \textbf{\em\&} Certifications} 

\begin{content}
% \vspace{0.05cm}

\begin{position}{Bloomberg for Education}{2024}{\normalfont\href{https://portal.bloombergforeducation.com/courses}{\texttt{Bloomberg Market Concepts (BMC)}}}{}{}
\item Bloomberg Market Concepts (BMC) is an e-learning course that provides a comprehensive understanding of essential concepts in finance, economics, and investment strategies, covering topics such as market structure, economic indicators, fixed income, equities, currencies, commodities, and portfolio management.
\end{position}

\begin{position}{Evidence in Governance and Politics}{2023}{\normalfont\href{https://egap.org/project/learning-days-13-latin-america-regional-hub-workshop/}{\texttt{Latin America Regional Hub (EGAP)}}}{}{}
  \item The \emph{EGAP's Learning Days Workshops} provide a comprehensive learning experience that includes design clinics, research presentations, hands-on experience with statistical analysis software, and topical lectures. The sessions covered topics such as randomization, causal inference, hypothesis testing, and impact evaluation.
\end{position}

\begin{position}{Instituto Nacional de Estadística y Geografía}{2017}{}{}{}
  \item \emph{Mapa Digital de México} (Taller Ejecutivo v.6), {\normalfont\href{https://drive.google.com/file/d/11P-V5IOrVxSAdumvZkqc6cNErlPHsWbA/view?usp=sharing}{\texttt{Dirección de Capacitación y Calidad}}}
  \item \emph{Productos de Información Estadística y Geográfica de México}, {\normalfont\href{https://drive.google.com/file/d/175VzjC148czXa4mLOryoo6QfAnEpCx_z/view?usp=sharing}{\texttt{Dirección de Capacitación y Calidad}}}
\end{position}

\end{content}

%%%%% %%%%% %%%%% Projects

\section{Projects \textbf{\em\&} Extracurriculars} 

\begin{content}
\vspace{0.05cm}

\begin{position}{La Gaceta de Ciencia Política}{2022}{\normalfont\href{https://gacetadecpol.wordpress.com}{\texttt{gacetadecpol.com}} $\sim$ \emph{Editorial Board}}{}{}
  \item Editorial Board Director of \emph{La Gaceta}, a print and digital publication for the dissemination of ideas and research in social sciences.
\end{position}

\begin{position}{Model United Nations}{2013 -- 2018}{}{}{}
  \item I participated for over 5 years in the planning, leadership, and organization of debate projects for university students, with a particular highlight being my involvement as a Committee member on multiple occasions at the Model United Nations of the \emph{H. Congreso de la Unión}, Congresmun. 
\end{position}

\sectionlineskip
\end{content}

%%%%% %%%%% %%%%% Technical Skills

\section{Technical Skills}

\begin{content}
% \vspace{0.05cm}

\begin{tabular}{ @{} >{\bf}l @{\hspace{6ex}} l }
  Programming Languages & R $\&$ RStudio (Advanced), Python (Novice), \LaTeX\ (Competent). \\ 
  Tools \textbf{\em\&} Technologies & MS Office (Advanced), Git \& Github (Competent), CartoDB (Competent). \\
  Languages & Spanish (Native), English (Advanced, C1).
\end{tabular}

\sectionlineskip
\end{content}

\end{document}

%%%%% %%%%% %%%%% Publciations 

%%% \noindent
%%% \renewcommand{\refname}{Publications}   % name of the reference section
%%% \bibliography{biblio.bib}               % bib file
%%% \bibliographystyle{abbrvnat}            % citation style
%%% \nocite{*}
%%% \sectionlineskip